From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-20 paper.tex
Minor tweaks

Neurons can be displayed with different levels of detail ranging from simple
spheres, cylinder-like geometric models and detailed polygonal
meshes. Advanced rendering techniques included are several types of parallel
rendering algorithms (such as sort-first and sort-last) and several algorithms
for transparency rendering that enable efficient and correct rendering of
scenes with great geometrical complexity and high depth
complexity. Transparency is particularly suitable for masking and highlighting
features of interest on the circuit. Ongoing work is a more scalable parallel
rendering algorithm specially suited for transparency. Tiled rendering is also
possible, which allows very high resolution renderings suitable for printing
at sizes larger than A0 (The original of \fig{fRTNeuron} left is a 36640$\times$26000 pixel image).

@@

\begin{figure}[h!t]\center
  \includegraphics[width=.45\columnwidth]{images/rtneuron1.png}\hfil
  \includegraphics[width=.45\columnwidth]{images/rtneuron2.png}
  \caption{\label{fRTNeuron}RTNeuron examples: membrame potential of a fraction of the neurons in a simulation (left) and a circuit visualization application showing a portion of a hippocampus model (right).}
\end{figure}

>>>>

Neurons can be displayed with different levels of detail ranging from simple
spheres, cylinder-like geometric models and detailed polygonal meshes. Advanced
rendering techniques included are several types of parallel rendering algorithms
(such as sort-first and sort-last) and several algorithms for transparency
rendering that enable efficient and correct rendering of scenes with great
geometrical complexity and high depth complexity. Transparency is particularly
suitable for masking and highlighting features of interest on the circuit.
Ongoing work is a more scalable parallel rendering algorithm specially suited
for transparency. Tiled rendering is also possible, which allows very high
resolution renderings suitable for printing at sizes larger than A0 (the
original of \fig{fRTNeuron} left is a 36640$\times$26000 pixel image).

@@

\begin{figure}[h!t]\center
  \includegraphics[width=.49\columnwidth]{images/rtneuron1.png}\hfil
  \includegraphics[width=.49\columnwidth]{images/rtneuron2.png}
  \caption{\label{fRTNeuron}RTNeuron rendering the simulated membrame potential of a fraction of the simulation~(left) and a circuit visualization application for hippocampus model validation~(right)}
\end{figure}
